Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2010-10-19 pugal-esco2010.tex
CiCP format

\documentclass[letterpaper,3p]{elsarticle}

\journal{Applied Mathematics and Computation}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{subfig}

\begin{document}
\begin{frontmatter}

@@

\author[unrme,tartu]{D.~Pugal}
\ead{david.pugal@gmail.com}

\author[unrmath,czech]{P.~Solin\corref{cor2}}
\ead{solin@unr.edu}

\author[unrme]{K.~J.~Kim\corref{cor1}}
\ead{kwangkim@unr.edu}

\author[tartu]{A.~Aabloo}
\ead{alvo@ut.ee}

\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
\address[unrmath]{Department of Mathematics and Statistics,
University of Nevada, Reno, NV, U.S.A.}
\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
\address[tartu]{Institute of Technology, Tartu University, Estonia}

\cortext[cor1]{Corresponding author}
\cortext[cor2]{Principal corresponding author}

@@

\begin{keyword}
  Ionic polymer-metal composites \sep IPMC \sep Nernst-Planck equation \sep Poisson equation 
  \sep finite element method \sep space-time adaptivity, multimesh \emph{hp}-FEM 
\end{keyword}

\end{frontmatter}

@@

\bibliographystyle{elsarticle-num}    % Bibliography: Author-Date system
\bibliography{pugal-esco2010}      % pls. call your database here

>>>>

\documentclass[mathpazo]{cicp}

%\journal{Applied Mathematics and Computation}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsrefs}
%\usepackage{subfig}

\begin{document}

@@

\author[Deivid Pugal et.~al.]{Deivid Pugal\affil{1}\comma\affil{2},
Pavel Solin\affil{3}\comma\affil{4}\comma\corrauth,
Kwang J. Kim\affil{1}, and Alvo Aabloo\affil{2}}

\address{\affilnum{1}\ Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{2}\ Institute of Technology, Tartu University, Estonia\\
\affilnum{3}\ Department of Mathematics and Statistics, University of Nevada, Reno, NV, U.S.A.\\
\affilnum{4}\ Institute of Thermomechanics, Prague, Czech Republic}

\emails{{\tt david.pugal@gmail.com} (D.~Pugal), {\tt solin@unr.edu} (P.~Solin),
	{\tt kwangkim@unr.edu} (K.~Kim), {\tt alvo@ut.ee} (A.~Aabloo)}

%\author[unrme,tartu]{D.~Pugal}
%\ead{david.pugal@gmail.com}
%
%\author[unrmath,czech]{P.~Solin\corref{cor2}}
%\ead{solin@unr.edu}
%
%\author[unrme]{K.~J.~Kim\corref{cor1}}
%\ead{kwangkim@unr.edu}
%
%\author[tartu]{A.~Aabloo}
%\ead{alvo@ut.ee}
%
%\address[unrme]{Mechanical Engineering Department, University of Nevada, Reno, NV, U.S.A.}
%\address[unrmath]{Department of Mathematics and Statistics,
%University of Nevada, Reno, NV, U.S.A.}
%\address[czech]{Institute of Thermomechanics, Prague, Czech Republic}
%\address[tartu]{Institute of Technology, Tartu University, Estonia}
%
%\cortext[cor1]{Corresponding author}
%\cortext[cor2]{Principal corresponding author}

@@

%\begin{keyword}
%\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
%finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
%\end{keyword}

%see http://www.ams.org/mathscinet/msc/msc2010.html?t=35Qxx&btn=Current

\ams{35Q84, 35Q05, 35J47}
\keywords{Ionic polymer-metal composites, IPMC, Nernst-Planck equation, Poisson equation,
finite element method, space-time adaptivity, multimesh \emph{hp}-FEM }
\maketitle

%\end{frontmatter}

@@

%\begin{thebibliography}{99}
%\bibitem{\ldots}..

%\end{thebibliography}

%\bibliographystyle{amsrs}    % Bibliography: Author-Date system
\bibliography{pugal-esco2010}      % pls. call your database here
